FitBit Analysis

### 2023-01-04 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
Update fitbit_paper.Rmd

### Wrist-worn devices as a new approach to assess physiological measures
"The use of physiological measures enabled us to get some insight into teachers’ affective responses without disrupting the teaching process (Mauss & Robinson, 2009) and to reduce issues with social desirability, retrospective bias, and high cognitive load (Becker et al., 2015; Goetz et al., 2015; Scollon et al.,2009; Wilhelm & Grossman, 2010). Moreover, we found that heart rate measures discriminated between both teachers, even when their interpersonal behavior during the lesson start was relatively similar."

@@

### Teachers' self-assessment of arousal during the teaching phase
The subject's self-assessment of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson. For this purpose, two numerical 11-point rating scales were used: _(1)_	The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption with the following question: "On a scale of 0-10: how disruptive did you find the event? 0 is not disruptive at all, 10 is extremely disruptive" _(2)_	The second rating scale assessed the teacher’s subjective perception of confidence in dealing with the disruptions during the lesson asked as follows: "How confident did you feel in dealing with this event on a scale of 0-10? 0 is not confident at all and 10 is extremely confident"
The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjetcts' self-assessment and emotional experience, and thus to make them measurable and comparable [@eid2015statistik; @doring2016empirische]. The gradations of the rating scale were unambiguous and the intervals between them identical. The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally to the experimenter.

@@

### Heart rate Data

@@

### Rating Scale Data

@@

# Discussion and implication
The analyses showed that wrist-worn fitness trackers are a suitable method to measure different phases of arousal in (prospective) teachers in laboratory settings, with clear effects visible even in intervals of just 10 minutes.

>>>>

### Wrist-worn devices as a new approach to assess physiological measures

@fuller2020reliability showed in their review article that wearable devices such as Fitbit watches are accurate and reliable for measuring heart rate in controlled settings.

"The use of physiological measures enabled us to get some insight into teachers’ affective responses without disrupting the teaching process (Mauss & Robinson, 2009) and to reduce issues with social desirability, retrospective bias, and high cognitive load (Becker et al., 2015; Goetz et al., 2015; Scollon et al.,2009; Wilhelm & Grossman, 2010). Moreover, we found that heart rate measures discriminated between both teachers, even when their interpersonal behavior during the lesson start was relatively similar."

@@

### Teachers' self-reported data of arousal during the teaching phase
The subject's self-reported data of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson. For this purpose, two numerical 11-point rating scales were used: _(1)_	The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption ("On a scale of 0-10: how disruptive did you find the event? 0 is not disruptive at all, 10 is extremely disruptive") _(2)_	The second rating scale assessed the teacher’s subjective perception of confidence in dealing with the disruptions during the lesson ("How confident did you feel in dealing with this event on a scale of 0-10? 0 is not confident at all and 10 is extremely confident").

The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjects' self-report and emotional experience, and thus to make them measurable and comparable [@eid2015statistik; @doring2016empirische]. The gradations of the rating scale were unambiguous and the intervals between them identical. The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally to the experimenter.

@@

### Heart rate data

@@

### Teachers' self-reported data of arousal during the teaching phase

@@

# Discussion and implications
The analyses showed that wrist-worn fitness trackers are a suitable method to measure different phases of arousal in (prospective) teachers in laboratory settings, with clear effects visible even in intervals of just 10 minutes.
